Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
comment on figure 7

\begin{figure}[t]
\center
\includegraphics[width = \textwidth]{figures/spontaneousSimilarity.png}
\caption{Computational model composed of two successive processing stages and alternative implementations.}
\label{fig:model}
\end{figure}

@@

>>>>

\begin{figure}[t]
\center
\includegraphics[width = \textwidth]{figures/spontaneousSimilarity.png}
\caption{Computational model composed of two successive processing stages and alternative implementations.
\vl{The boxes "features" and "projection" should be renamed "feature extraction" and "metric learning".
This figure is not very useful since it does not distinguish training time from prediction time.
@figure}}
\label{fig:model}
\end{figure}

@@

\vl{I would suggest trying to avoid the invention of the "TST" acronym for "temporal scattering transform" if possible.
This acronym does not already exist in the relevant literature. @writing}
